Real Estate

### 2022-11-08 src/real_estate.Rmd
cleaning up code

```{r}
# normalize columns into new data table
n_MSA_realEstate <- MSA_RE_ratios %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_avg_rent_to_income = (avg_rent_to_income- min(avg_rent_to_income, na.rm = TRUE)) / (max(avg_rent_to_income, na.rm = TRUE) - min(avg_rent_to_income, na.rm = TRUE))) %>% 
  mutate(n_med_rent_to_income = (med_rent_to_income- min(med_rent_to_income)) / (max(med_rent_to_income) - min(med_rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice))) %>% 
  mutate(n_avg_occupancy = (avg_occupancy_21 - min(avg_occupancy_21, na.rm = TRUE)) / (max(avg_occupancy_21, na.rm = TRUE) - min(avg_occupancy_21, na.rm = TRUE))) %>% 
  mutate(n_rent_change = (rent_change21_22 - min(rent_change21_22, na.rm = TRUE)) / (max(rent_change21_22, na.rm = TRUE) - min(rent_change21_22, na.rm = TRUE)))

>>>>

```{r}
# normalize columns into new data table
n_MSA_realEstate <- MSA_RE_ratios %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_avg_rent_to_income = (avg_rent_to_income- min(avg_rent_to_income, na.rm = TRUE)) / (max(avg_rent_to_income, na.rm = TRUE) - min(avg_rent_to_income, na.rm = TRUE))) %>% 
  mutate(n_med_rent_to_income = (med_rent_to_income- min(med_rent_to_income)) / (max(med_rent_to_income) - min(med_rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice))) %>% 
  mutate(n_avg_occupancy = (avg_occupancy_21 - min(avg_occupancy_21, na.rm = TRUE)) / (max(avg_occupancy_21, na.rm = TRUE) - min(avg_occupancy_21, na.rm = TRUE))) %>% 
  mutate(n_rent_change = (avg_rent_change - min(avg_rent_change, na.rm = TRUE)) / (max(avg_rent_change, na.rm = TRUE) - min(avg_rent_change, na.rm = TRUE)))
